Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-13 design.tex
submitted

A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$. This available capacity will be restored back to after the finish of $t_{ij}$ part.

@@

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.

@@

% \subsubsection{Provider respond to type-matched job} % (fold)
% \label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ respond to $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ respond to $sc_l$
\suspend{asparaenum}
If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ respond to $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

% \subsubsection{Demander select from machine candidates} % (fold)
% \label{ssub:selection_in_resource_candidates_for_service_call}
Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:

@@

% \subsubsection{Provider assign task to selected machine} % (fold)
Apart from $mr_k$ assign $t_{ij}$ when selected as we explained in \autoref{subs:assign_in_select_resource}, there are 2 other cases in incubation mode:

\begin{asparaenum}
\item Assign $sc_l$ to $mr_k$
\suspend{asparaenum}
If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict than that in \autoref{subs:assign_in_select_resource}, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one. Then, the provider of $mr_k$ should change the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
\end{equation}
and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
\end{equation}
And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
\resume{asparaenum}
\item Assign $t_{ij}$ to $ms_l$
\end{asparaenum}
Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.
% \begin{subnumcases}{}
% \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
% \end{subnumcases}

@@

\subsection{Outsourcing mode} % (fold)
\label{sub:outsource_mode}
Outsourcing mode is one extension on the original mode and will be active when incubation mode is on that only service can perform this procedure. As shown in \autoref{fig:outsourcemode},
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
%     \caption{Outsourcing mode}
%     \label{fig:outsourcemode}
% \end{figure}
the idea of outsourcing for service is to republish active or inactive task to platform again in order to reduce its job queue length to enhance the probability to be selected by new tasks. For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status decreases. This decision highly depends on the estimation of other resources and services' performance status. Outsourcing mode makes it possible to paralleled process one job.
% subsection outsource_mode (end)

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members. As shown in \autoref{fig:metabolismmode},
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
%     \caption{Metabolism mode}
%     \label{fig:metabolismmode}
% \end{figure}
we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.

@@

The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs. \autoref{eq:subsequence} makes sure that all predecessors of each job finished before the job itself. \autoref{eq:alreadydefined} means that the finish time of activate job is determined. \autoref{eq:caplimitwithtime} makes sure the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
solved with mixed integer programming (MIP) techniques.

>>>>

A provider makes decision at time $\tau\ge r_i$ to respond  to task if the belonging resource $mr_k$ was type-matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, the provider will respond to the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ is finally selected, available capacity of $mr_k$ will change to $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$. This available capacity will be restored after the finish of $t_{ij}$ part.

@@

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} ensures that resource capacity is capable to process the task-part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variables, the demander should make decision to select resources in each type.

@@

% \subsubsection{Provider respond to type-matched job} % (fold)
% \label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ respond to $t_{ij}$ as we explained above, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ respond to $sc_l$
\suspend{asparaenum}
If $mr_k$ was type-matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will respond to the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be restored even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ respond to $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type-matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will respond to $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

% \subsubsection{Demander select from machine candidates} % (fold)
% \label{ssub:selection_in_resource_candidates_for_service_call}
Apart from demander of $t_{ij}$ select $mr_k$ that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:

@@

% \subsubsection{Provider assign task to selected machine} % (fold)
Apart from $mr_k$ assign $t_{ij}$, there are 2 other cases in incubation mode:

\begin{asparaenum}
\item Assign $sc_l$ to $mr_k$
\suspend{asparaenum}
If $mr_k$ is selected by provider of $sc_l$ at time $\tau$, the assign condition is more restrict, it should be changed into $\abs{\mathcal{L}_{k,\tau}} = \abs{\mathcal{G}_{k,\tau}} = \abs{\mathcal{H}_{k,\tau}} = 0$, for the capacity dominance feature of service-call, we need to assign this type of job one by one. Then, the provider of $mr_k$ should change the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{H}_{k,\tau}
\end{equation}
and all the task assign after $\tau$, we say $\tau'>\tau$ will set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau'},sc \text{ is service-call} \right\} \cup \mathcal{H}_{k,\tau'}
\end{equation}
And $A_{k,\tau}$ will be changed with the same amount in \autoref{eq:capq}--\ref{eq:cap0}.
\resume{asparaenum}
\item Assign $t_{ij}$ to $ms_l$
\end{asparaenum}
Assign $t_{ij}$ to $ms_l$ is very simple and there will be no semi-active status for $t_{ij}$, hence it will add to $\mathcal{G}_{k,\tau}$ if $\abs{\mathcal{G}_{k,\tau}}=0$, or to $\mathcal{L}_{k,\tau}$ otherwise.
% \begin{subnumcases}{}
% \mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_{l}\} & if $\abs{\mathcal{G}_{k,\tau}}=0$ \\
% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{sc_{l}\} & otherwise
% \end{subnumcases}

@@

\subsection{Outsourcing mode} % (fold)
\label{sub:outsource_mode}
Outsourcing mode is one extension for the original mode when incubation mode is applied. As outsourcing part shown in \autoref{fig:modes},
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.7\textwidth}{!}{\input{figures/outsource}}
%     \caption{Outsourcing mode}
%     \label{fig:outsourcemode}
% \end{figure}
the idea of outsourcing for service is to republish active or inactive task to platform again in order to reduce its job queue length to enhance the probability to be selected by new tasks. For each single task $t_j\in\mathcal{L}_{l,\tau}\cup\mathcal{G}_{l,\tau}$, the only condition to make the outsource decision is that if the maximum delay($f_j-p_j-r_j$) of task in both status decreases. This decision highly depends on the estimation of other resources and services' performance status. Outsourcing mode makes it possible to paralleled process one job.
% subsection outsource_mode (end)

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension for the original mode to control the number of individual in the system by both restrict the arrival and eliminate the current members. As metabolism part shown in \autoref{fig:modes},
% \begin{figure}[htbp]
%     \centering
%     \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
%     \caption{Metabolism mode}
%     \label{fig:metabolismmode}
% \end{figure}
we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.

@@

The schedule aim for each resource \autoref{eq:scheduleaim} is to minimum the maximum delay of jobs. \autoref{eq:subsequence} ensures that all predecessors of each job finished before the job itself. \autoref{eq:alreadydefined} means that the finish time of activate job is determined. \autoref{eq:caplimitwithtime} ensures the capacity restriction at every time period and \autoref{eq:finishconstrain} defines the extreme situation of the finish time.
Since \autoref{eq:caplimitwithtime} is a time dependent function, the schedule model cannot be
solved with mixed integer programming (MIP) techniques.

### 2016-09-13 discussion.tex
submitted

% !TEX root = Eco-Model.tex
\section{Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}
We only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions. The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
% section contributions_limitations_and_future_research (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Conclusions, Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}
In the extended modes we designed for cloud manufacturing ecosystem, incubation mode can realize a feasible solution for the formation of manufacturing service, shorten the job queue length and reduce the resource idle rate; outsourcing mode can cut down the amount of registered resource; metabolism mode can also cut down the amount of registered resource in price of a little higher resource idle rate. The combine of incubation and metabolism mode makes the maintenance of platform much easier.
However, we only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions. The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
% section contributions_limitations_and_future_research (end)

### 2016-09-13 result.tex
submitted

Individuals in the manufacturing ecosystem are: \begin{inparaenum}[1)]
\item autonomous and self-directed,
\item social, interacting with other entities,
\item controlled by the environment,
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision-makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} is suitable for the study in such a complex system. With the help of Repast Simphony \cite{North2013} package was utilized in this experiment.

@@

\subsection{Experiments} % (fold)
\label{ssub:case_design}
RanGen \cite{Demeulemeester2003} was used to generate order dataset in the well-known Patterson format with the parameters setting listed in \autoref{tab:generalparameter}.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%
We assume that providers and demanders are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the average coming resource capacity rate in average to prevent the task explosion, and we make sure that,
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}

We design experiments in groups to validate incubation, outsourcing and metabolism mode \autoref{tab:grouping}, 10 datasets represent 10 types of orders, and each of them contains 10 tasks with different configuration on 12 types of resources to perform with.

>>>>

Because of the  autonomous and self-directed features of individuals in the manufacturing ecosystem, we use agent-based modeling and simulation(ABMS) technique \cite{Macal2009,north2007managing} to study such a complex system. Repast Simphony \cite{North2013} package was utilized in this experiment.

@@

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We design experiments to repeatedly simulate the operating of ecosystem with 6 different mode combinations in \autoref{tab:grouping} group by group, which are the prototypes of feasible cloud manufacturing operating modes. Every single simulation goes with the main flow as show in \autoref{fig:originmode}. We use  RanGen \cite{Demeulemeester2003} to generate dataset in the well-known Patterson format as the the continuously arriving order for the simulation input, related parameter settings are listed in \autoref{tab:generalparameter}.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Order generating parameters setting}
    \begin{tabular}{cccccccccc}
    \toprule
    \textbf{$n_a$} & \textbf{OS} & \textbf{CI} & \textbf{$n_r$} & \textbf{RF} & \textbf{RC} & \textbf{$\lambda_d$} &\textbf{$\lambda_p$} & \textbf{$C_{k,0}$}\\
    \midrule
     10  &   0.3    &  [2,3]     &   12     &  0.3     &   0.5  & 0.2 & 0.3  & [20,30] \\
    \bottomrule
    \end{tabular}%
    {\footnotetext{\tiny The meaning of the first 5 parameters are defined in \cite{Demeulemeester2003}, $\lambda$ is the parameters of the arrival of user in simulation, $C_{k,0}$ is the initial capacity for $mr_k$}
    }
  \label{tab:generalparameter}%
\end{table}%

We assume that providers and demanders are arriving as the Poisson process, in order to make sure the coming need resource capacity rate will not exceed the average coming resource capacity rate in average to prevent the task explosion, and we make sure that,
\begin{equation}
\lambda_d n_a n_r \cdot RF \cdot RC < \lambda_p \bar C_{k,0} \label{eq:balance}
\end{equation}
